Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-07-28 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:07:23	20:45:57	(Thu23.Jul)
la2pdf commit - 2015:07:24	12:11:09	(Fri24.Jul)
la2pdf commit - 2015:07:24	12:42:40	(Fri24.Jul)
la2pdf commit - 2015:07:28	19:48:39	(Tue28.Jul)

@@

>>>>

3rd order Maclaurin / Tayler approximation
\begin{align}
\phi_\text{-3dB bounds} \approx -0.002894\beta^3 + 0.02451\beta^2 + -0.01308\beta + 0.2980
\end{align}

@@

\begin{figure*}[htb!]\centering%
\includegraphics[width=\linewidth]{gfx/mvdr_selected_windows.eps}%
\caption{Typical window responses for a robust MVDR. The dashed red line is the response of an unsteered rectangular window on the full array. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3dB in highlight. The phase varies mostly in highlight. }\label{mvdr_selected_windows}
\end{figure*}

What's up?

\begin{figure*}[htb!]%\centering%
\includegraphics[width=.5\linewidth]{gfx/oversampling_mosaic_bounds.eps}%
\caption{Steering within -3dB for each window}\label{mvdr_selected_windows}
\end{figure*}

\begin{figure*}[htb!]%\centering%
\includegraphics[width=.5\linewidth]{gfx/calc_kaiser_3dB.pdf}%
\caption{Steering within -3dB for each window}\label{mvdr_selected_windows}
\end{figure*}
